% \setcounter{chapter}{15}
\appendix
% \renewcommand{\thechapter}{P}

\chapter{Publication list}\label{sec:publications}

\section*{Journal publications}

Nash, B., Goldring , N., Edelen, J., Webb, S. and \underline{Celestre, R.}, (2021). Propagation of partially coherent radiation using Wigner functions. \textit{Physical Review Accelerators and Beams}, \textbf{24}(1), 010702. 

Qiao, Z., Shi, X., \underline{Celestre, R.} and Assoufid, L. (2020). Wavelet-transform-based speckle vector tracking method for X-ray phase imaging. \textit{Optics Express}, \textbf{28}(20), 1094. 

\underline{Celestre, R.}, Berujon, S., Roth, T., Sanchez del Rio, M. and Barrett, R. (2020). Modelling phase imperfections in compound refractive lenses. \textit{Journal of Synchrotron Radiation}, \textbf{27}(2), 305–318. 

Berujon, S., Cojocaru, R., Piault, P., \underline{Celestre, R.}, Roth, T., Barrett, R. and Ziegler, E. (2020). X-ray optics and beam characterization using random modulation: experiments. \textit{Journal of Synchrotron Radiation}, \textbf{27}(2), 293–304.

Berujon, S., Cojocaru, R., Piault, P., \underline{Celestre, R.}, Roth, T., Barrett, R. and Ziegler, E. (2020). X-ray optics and beam characterization using random modulation: theory. \textit{Journal of Synchrotron Radiation}, \textbf{27}(2), 284–292.

Sanchez del Rio, M., \underline{Celestre, R.}, Glass, M., Pirro, G., Herrera, J. R., Barrett, R., da Silva, J. C., Cloetens, P., Shi, X. and Rebuffi, L. (2019). A hierarchical approach for modeling X-ray beamlines: application to a coherent beamline. \textit{Journal of Synchrotron Radiation}, \textbf{26}(6), 1887–1901.

Chubar, O. and \underline{Celestre, R.} (2019). Memory and CPU efficient computation of the Fresnel free-space propagator in Fourier optics simulations. \textit{Optics Express}, \textbf{27}(20), 28750. 

\section*{Conference proceedings}

\underline{Celestre, R.}, Chubar, O., Roth, T., Sanchez del Rio, M. and Barrett, R. (2020). Recent developments in x-ray lenses modelling with SRW. \textit{Proc. SPIE 11493, Advances in Computational Methods for X-Ray Optics V}, 11493-17.

Chubar, O., Wiegart, L., Antipov, S., \underline{Celestre, R.}, Coles, R., Fluerasu, A. and Rakitin, M. (2020).  Analysis of hard x-ray focusing by 2D diamond CRL. \textit{Proc. SPIE 11493, Advances in Computational Methods for X-Ray Optics V}, 11493-20.

Nome, R., Giles, C., \underline{Celestre, R.}, Tasca, K., Dias, C., Vescovi, R., Faria, G. and Ferbonink, G. (2018). Compact arrangement for femtosecond laser induced generation of broadband hard x-ray pulses. \textit{High-Brightness Sources and Light-Driven Interactions}, ET1B.3.

